The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Sanity check
updates
Test
Updates to Section 3 of the paper

@@

\subsection*{The option {\tt UseSpecialAlgorithms} for the {\tt fpt} function}

@@

If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the four forementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing.  If this command returns {\tt true}, the $F$-pure threshold can easily be computed, and {\tt fpt} returns this value.  For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see the end of this section.

\subsection*{Searching for the $F$-pure threshold when no special algorithm applies}

@@

\subsection*{The function {\tt isSimpleNormalCrossings}}
As mentioned earlier, 
when the option {\tt useSpecialFunctions} for the function {\tt fpt} is set to {\tt true}, if the polynomial $f$ is neither a diagonal polynomial, a binomial, or a form in two variables, there is a final check to verify whether $f$ is a product of factors in simple normal crossing.

>>>>

SANITY TEST FOR DANIEL
DANIEL MODIFYING THE PAPER AFTER EMILY

@@

\subsection{The option {\tt UseSpecialAlgorithms} for the {\tt fpt} function}

@@

If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the four forementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing.  If this command returns {\tt true}, the $F$-pure threshold can easily be computed, and {\tt fpt} returns this value.  For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see Section \ref{subsec.SNC}.

\subsection{How {\tt fpt} proceeds when no special algorithm applies}

@@

\subsection{The function {\tt isSimpleNormalCrossings}} \label{subsec.SNC}
As mentioned earlier, 
when the option {\tt useSpecialFunctions} for the function {\tt fpt} is set to {\tt true}, if the polynomial $f$ is neither a diagonal polynomial, a binomial, or a form in two variables, there is a final check to verify whether $f$ is a product of factors in simple normal crossing.
